\addcontentsline{toc}{subsection}{Pathing}
\LARGE \textbf{Pathing} \normalsize

RON needs to find their way to the ballot box, to vote in the SU elections!
They know their way around campus, so from any starting square can always take the fastest available route to the square with the ballot box.

But RON is a robot; they can only move horizontally or vertically between squares.
It's also been raining recently, and two of the squares are now covered in deadly dihydrogen monoxide \dots
RON will short-circuit the second they step on one! 

How many moves will RON need to make in order to vote?

\vspace{8pt}
\hrule

\textbf{Input}

The first line of the input contains an integer $t$, denoting the number of test cases.

The $t$ remaining lines of the input contain 8 space-separated integers:
\begin{itemize}
    \item The first pair represents RON's starting coordinates $(s_x, s_y)$.
    \item The next pair represents the coordinates of the ballot box $(f_x, f_y)$.
    \item The final two pairs represent the coordinates of the deadly tiles $(a_x, a_y), (b_x, b_y)$.
\end{itemize}

\textbf{Constraints}

\begin{itemize}
    \item The $x$ and $y$ components of each coordinate will be between $0$ and $10^9$.
    \item Note that RON may still travel outside of these coordinate bounds.
\end{itemize}

\textbf{Output}

Each of the $t$ output lines should consist of a single integer, 
representing the number of times RON needs to move between sqaures in order to reach the ballot box.

\vspace{8pt}
\hrule

\textbf{Example}

\begin{table}[h]
    \centering
    \begin{tabular}{|p{0.4\linewidth}|p{0.4\linewidth}|}
        \hline
        Input & Output \\
        \hline
        4 \newline 0 0 2 2 0 2 2 0 \newline 0 0 2 2 0 1 1 0 \newline 1 1 1 1 0 1 1 0 \newline 0 0 0 2 0 1 1 2 & 
        4 \newline 6 \newline 0 \newline 4 \\
        \hline
    \end{tabular}
\end{table}

There are 4 test cases:

\begin{enumerate}
    \item There is an unobstructed shortest path from $(0, 0)$ to $(2, 2)$, we move 4 squares.
    \item We are obstructed by $(0, 1)$ and $(1, 0)$, so go around and move 6 squares.
    \item We are already at our destination without needing to move.
    \item We take the shortest detour around the tiles, which requires 4 moves.
\end{enumerate}