\addcontentsline{toc}{subsection}{Shifty}
\LARGE \circled{2} \textbf{Main Problem - Shifty} \normalsize

{\itshape What do you mean, "it's not a real metric"?}

Okay so, remember that word metric from the introductory problem? 
As it turns out, it wasn't very useful - most pairs of words tend not to have the same length.

That's why I've come up with the new and improved \texttt{SHIFT} Two (\texttt{SHIFT-T} for short)! 
It adds two more operations to the mix:

\begin{enumerate}
    \setcounter{enumi}{2}
    \item Duplicate the left-most letter
    \item Delete the left-most letter
\end{enumerate}

These new rules can be applied with the others in any order. See? It's useful now!
Now we just need someone to calculate the \texttt{SHIFT-T} distance between two words...

\vspace{8pt}
\hrule

\textbf{Input}

The first line of the input contains an integer $t$, denoting the number of test cases.
\\ The next $t$ lines of the input consist of two space-separated strings $w_1$ and $w_2$.

\textbf{Constraints}

\begin{itemize}
    \item $1 \leq t \leq 1000$
    \item $1 \leq |w_1|, |w_2| \leq 30$
    \item $w_1$ and $w_2$ will be uppercase.
\end{itemize}

\textbf{Output}

$t$ lines, each consisting of a sequence of $s$ space separated strings. 

This sequence must start with $w_1$, end with $w_2$, 
and describe all the intermediate strings resulting from the application of valid \texttt{SHIFT-T} operations. 

Although there may be multiple valid sequences of words,
the length of your sequence should not need to exceed $m = 13 \cdot \max{(|w_1|, |w_2|)}$.

\vspace{8pt}
\hrule

\textbf{Scoring}

\begin{itemize}
    \item $-100$ Points for an invalid step sequence.
    \item $\max{\left(0, m - s + 1\right)}$ Points for a valid step sequence.
\end{itemize}

\vspace{8pt}
\hrule

\textbf{Example}

\begin{table}[h]
    \centering
    \begin{tabular}{|p{0.2\linewidth}|p{0.6\linewidth}|}
        \hline
        Input & Output \\
        \hline
        5 \newline READ REED \newline MADE MAD \newline MAD MADE \newline A BABY \newline PAID FEED & 
        \text{} \newline READ REBD RECD REDD REED \newline MADE EMAD MAD \newline MAD DMA EMA EEMA DEMA ADEM MADE \newline A AA AAA AAAA BAAA BABA BABZ BABY \newline PAID AID ID D DD ED EED EEED FEED \\
        \hline
    \end{tabular}
\end{table}

This would return a score of 233. Can you do better?

To verify your submission for the contest, or serve as proof you've taken part, DM your username, score, and the script you used to our shared discord account - \textbf{UWCS\#3568}.
\\ \texttt{Good luck, and have fun!}