\addcontentsline{toc}{subsection}{Shift}
\LARGE \textbf{Problem 1 - Shift} \normalsize

{\itshape We can do this the easy way...}

For a computer to  automatically check for incorrect spelling, 
it needs a method to guess which word we were attempting to write.
One popular way is by using the Levenshtein word metric - and suggesting the words returning the lowest score.

Let's make our own word metric! It's called SHIFT\footnote{If spoken aloud, note that the F is pronounced silently.}, and consists of two operations:

\begin{enumerate}
    \item Shift a letter a position up or down the alphabet (with wraparound)
    \item Shift a letter on either edge of a word to the other side.
\end{enumerate}

The SHIFT distance is defined as the minimum number of operations we need to make to get from one word to another.

Given two words of the same length, what is the SHIFT distance between them?
% Maybe include an image too?

\vspace{8pt}
\hrule

\textbf{Input}

The first line of the input contains an integer $t$, denoting the number of test cases.

The next $t$ lines of the input consist of two space-separated strings $w_1$ and $w_2$.

\textbf{Constraints}

\begin{itemize}
    \item $1 \leq |w_1| = |w_2| \leq 13$
    \item $w_1$ and $w_2$ will be uppercase.
\end{itemize}

\textbf{Output}

$t$ lines each consisting of a single integer, the SHIFT distance between $w_1$ and $w_2$.

\vspace{8pt}
\hrule

\textbf{Example}

\begin{table}[h]
    \centering
    \begin{tabular}{|p{0.4\linewidth}|p{0.4\linewidth}|}
        \hline
        Input & Output \\
        \hline
        5 \newline READ REED \newline ZERO HERO \newline PAID FEED \newline WORDS SWORD \newline REDDIT CRINGE & 
        \text{} \newline 4 \newline 8 \newline 18 \newline 1 \newline 31 \\
        \hline
    \end{tabular}
\end{table}


There are 5 test cases:

\begin{enumerate}
    \item We shift the A in READ down by 4 to get to REED.
    \item We shift the Z in ZERO down by 8 to get to HERO.
    \item We shift P up by 10, A down by 4, and I up by 4 to get to FEED.
    \item We shift WORDS to the right by 1, and it immediately becomes SWORD.
    \item We shift to the left by 3 to get DITRED, then perform 28 letter shifts.
\end{enumerate}