\togglefalse{IsScore}
\problem{1}{Find Milk}{Keegan R}
{How long does it take for a joke to die?}

The exec were busy preparing for Milk Mondays, the greatest event known to mankind.
But, oh no!
The milk (all four characters of it) got spilt into a pool of letters.

\begin{center}
    \Huge \bfseries \textcolor{uwcsblue}{M}AKESAWH\textcolor{uwcsblue}{I}TE\textcolor{uwcsblue}{L}A\textcolor{uwcsblue}{K}E
\end{center}

Don't cry over spilt milk.
Instead, let's bring it back together: find the shortest substring that contains all of the letters "M", "I", "L", and "K".
Quick, before it goes off!

\vspace{8pt}
\hrule

\textbf{Input}

The first line of the input contains an integer $n$, denoting the number of test cases.

The next $n$ lines each consist of a single string of uppercase letters, $s$.

\textbf{Constraints}
\begin{equation*}
    1 \leq n \leq 10^3 \qquad
    4 \leq |s| \leq 10^4
\end{equation*}

At least one "M", "I", "L", and "K" will be present in $s$.

\textbf{Output}

$n$ lines, each consisting of two space-separated integers: 
both the start and end indices (zero-indexed) of the smallest substring in $s$ containing the characters "M", "I", "L", "K".

\vspace{8pt}
\hrule

\textbf{Example}

\begin{table}[h]
    \centering
    \begin{tabular}{|p{0.4\linewidth}|p{0.4\linewidth}|}
        \hline
        Input & Output \\
        \hline
        \texttt{3\newline
        HIJKLMN\newline
        KLAAAMIIKAL\newline
        MILKMLIKMIKLIMLK\newline}
        & 
        \texttt{1 5\newline 
        5 10\newline
        3 6\newline}
        \\
        \hline
    \end{tabular}
\end{table}

A few notes about these test cases:

\begin{enumerate}
    \item Only the first and last character are excluded. Remember: order doesn't matter.
    \item Although "KLAAAMI" contains MILK, "MIIKAL" is shorter.
    \item Sometimes, there may be multiple valid answers.
\end{enumerate}